---
title: "Homework-2"
format: html
editor: visual
---
#Packages

##Question 1


```{r}
#| eval = FALSE
install.packages("aRtsy")
```

#install.packages is a collection of function and tools while a library is a place packages are stored.

\newpage

##Question 2 
```{r}
library(aRtsy)
#Collatz conjecture is a mathmatical riddle where you take any positive whole number and follow two simple rules over and over and will eventually end up back at 1. 
```
$$ f(n)
\begin{cases}
\frac{n}{2} & \text{if } n \text{ is even} \\
3n + 1 & \text{if } n \text{ is odd}
\end{cases} $$

\newpage 

##Question 3
```{r}
canvas_collatz(
  colors = c("blue"),
  n=10
)
# canvas collatz calls for the specific artwork. Colors is the type of color to draw the branches with. And n=10 is the telling r to pick 10 random numbers bending the lines each time its even or odd. 
```
```{r}
set.seed(7)
```

##B
# You get different outputs because we told r to pick 10 random images to output. 
# This may be troublesome because its not reproducible, when rendering different outputs are produced meaning you will see something different then I will. 
